Introducing the JuliaHealth Observational Health Research Subecosystem

### 2023-12-28 header.tex
New title details

\title{Developing Observational Health Research Capacity in the Julia Ecosystem}

@@

\hypersetup{
pdftitle = {Developing Observational Health Research Capacity in the Julia Ecosystem},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {Jacob S. Zelko, Fareeda Abdelazeez, Malina Hy, Varshini Chinta, Jay Sanjay},
pdfkeywords = {Observational Health, OMOP Common Data Model, Database Management, Characterization},
}

>>>>

\title{Introducing the JuliaHealth Observational Health Research Subecosystem}

@@

\hypersetup{
pdftitle = {Introducing the JuliaHealth Observational Health Research Subecosystem},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {Jacob S. Zelko, Fareeda Abdelazeez, Malina Hy, Varshini Chinta, Jay Sanjay},
pdfkeywords = {Observational Health, OMOP Common Data Model, Database Management, Characterization},
}
